Increasing User Engagement in a Volunteer-Based Ephemeral Evolutionary Computation System

### 2017-11-03 2017-EUROPAR/Gamification/paper.tex
Revising abstract for EvoPar

One way of creating distributed computing system is to use volunteers who
provide their own computing resources or storage to contribute to a common effort.
By running a script in a web page, collaboration is straightforward, but also ephemeral.
Resources depend on the amount of time a user lends, which means that 
the user has to be kept engaged to obtain as many computing cycles as
possible. In this paper, we analyze a volunteer-based evolutionary computing system called
NodIO with the objective of discovering rules that encourage volunteer
participation thus increasing the overall computing power. We present the results of
an experiment where a gamification technique is applied by adding a leader-board 
showing the top scores achieved by registered contributors. In the NodIO system volunteers can
participate without the need to create an account, so the question was
if the need to register would have a negative impact on user participation. 
The experiment results show that even if only a small percentage of users created an account,
those participating in the competition provided around 90\%.

>>>>

Distributed computing systems can be created using volunteers who
provide their own computing resources or storage to contribute to a common effort. They can, for instance,  run a script embedded in a web page, collaboration is straightforward, but also ephemeral, with resources depending on the amount of time a user lends; this  implies that 
the user has to be kept engaged so as to obtain as many computing cycles as
possible. In this paper, we analyze a volunteer-based evolutionary computing system called
NodIO with the objective of discovering rules that encourage volunteer
participation thus increasing the overall computing power. We present the results of
an experiment where a gamification technique is applied by adding a leader-board 
showing the top scores achieved by registered contributors. In the NodIO system volunteers can
participate without the need to create an account, so the question was
if the need to register would have a negative impact on user participation. 
The experiment results show that even if only a small percentage of users created an account,
those participating in the competition provided around 90\%.
